\documentclass[usenatbib]{mn2e}
\usepackage{float}
\usepackage[pdftex]{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{rotating}
\newcommand{\ol}[1]{ {\overline{#1}}}
\newcommand{\lu}{\,h^{-1}{\rm kpc}}
\renewcommand{\vec}[1]{ {\bmath #1} } 
\newcommand{\e}{{\rm e}}
\newcommand{\dd}{{\rm d}}
\newcommand{\ap}[1]{\textcolor{magenta}{#1}}
\def\gsim{ \lower .75ex \hbox{$\sim$} \llap{\raise .27ex \hbox{$>$}} }
\def\lsim{ \lower .75ex \hbox{$\sim$} \llap{\raise .27ex \hbox{$<$}} }

% landscape table
\usepackage{lscape}

% Individual page for figures
\usepackage{afterpage}

% Fancy merger rate symbol:
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[amssymb]{SIunits} 

% Make font much more compact
\usepackage{times}

% Compact lists (compactitem):
\usepackage{paralist}

% References highlighted in blue (include "draft" option for troubleshooting)
\usepackage[bookmarks,bookmarksnumbered,colorlinks=true,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{color}

% Line break inside table cell
\usepackage{pbox}

% Vertical spaces in table
\usepackage{booktabs}

% Tables with notes, etc.
\usepackage[flushleft]{threeparttable}

% Blocks of comments
\usepackage{comment} 

% Color highlighting
\definecolor{darkgreen}{rgb}{0.0, 0.5, 0.0}
\newcommand{\highlight}[1]{{\color{darkgreen} #1}}

% Custom commands, to be used inside math environment:
\newcommand{\Msun}{{\rm M_{\odot}}}

\setlength{\topmargin}{-1.2cm}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\newcommand{\Matrix}[1]{\mathsf{#1}}



\usepackage{booktabs}
\usepackage{hhline}
\usepackage{breqn}
\usepackage{standalone}
\usepackage{dcolumn}
	\newcolumntype{d}[1]{D{.}{.}{#1}}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{microtype}
% \usepackage{algpseudocode}
\usepackage[]{algorithm2e}
\usepackage[update,prepend]{epstopdf}
\epstopdfsetup{outdir=./figures/finalized/}
% the search path of the figures for this latex file 
% REMEMBER to add / at the END of the path
\graphicspath{{figures/finalized/}}
% \graphicspath{{./figures/finalized}{figures/drafts/}}

\newcommand{\mc}[1]{\multicolumn{1}{c}{#1}} % handy shortcut macro
%-----------------------------------------------------------------------
\def\Hmat{\mathbf{\it H}}
\def\apjl{ApJL }
\def\aj{AJ }
\def\apj{ApJ }
\def\pasp{PASP }
\def\spie{SPIE }
\def\apjs{ApJS }
\def\araa{ARAA }
\def\aap{A\&A }
\def\nat{Nature }
\def\mnras{MNRAS }
\def\mnrasl{MNRASL }
\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
\providecommand{\adsurl}[1]{\href{#1}{ADS}}
\providecommand{\ISBN}[1]{\href{http://cosmologist.info/ISBN/#1}{ISBN: #1}} 
%-----------------------------------------------------------------------
\title[
	The offsets between the galaxies and the dark matter in the galaxy clusters of the Illustris simulation]
{The offsets between the light and the dark matter	in the galaxy clusters of
the Illustris simulation}
\author[Karen Y. Ng et al.]{Karen Y. Ng,$^{1}$
	Annalisa P. Pillepich,$^{2}$ 
	William A. Dawson,$^{3}$ 
	D. Wittman,$^{1}$
	\newauthor Lars Hernquist$^{2}$
}
\begin{document}
\date{arXiv} \pagerange{\pageref{firstpage}--\pageref{lastpage}}
\pubyear{2015} \maketitle\label{firstpage}
\begin{abstract} 
	Assuming that dark matter has a zero self-interacting cross section, how likely is
	it for us to see the reported offset values between dark matter and galaxies 
	from real data of merging galaxy clusters? 
	This paper formulates a hypothesis test using cluster data in the cosmological 
	simulation, the Illustris simulation to answer the question. 
	We examined the hypothesis using most of the commonly use galaxy summary 
	statistics, including the
	luminosity peak, number density peak, shrinking aperture peak, centroid and
	the brightest cluster galaxy (BCG). 	
	We found that the choice of summary statistic to affect the offset
	value significantly with the BCG and the luminosity peak giving the tightest
	68-th percentile offsets levels.  
	Out of the 15 reported offset from observed merging clusters
	that we examined, 13 of
	them are consistent with the Illustris offset levels to 2-sigma 
	(95-th percentile) level. Although two of the reported offsets from inferred
	from luminosity peaks lie outside the 99-th percentile level, it is unclear
	if the large reported offset discrepancy is due to different ways of
	determining the smoothing kernel width. 
	We also identified that the long
	tail of the offset distribution of the BCG to be due to projected 
	substructures. In general, galaxy summary statistic such as
	shrinking aperture, number density and centroid give large bias of $\sim$ 50
	$-$ 100 kpc at
	the 68-th percentile level, even for clusters with only one dominant 
	mass component. Out of all the summary statistic that use a population of galaxies, 
	the luminosity peak is the most 
	robust to substructures if a proper statistical procedure is used to determine
	the smoothing bandwidth for the luminosity map.
\end{abstract}

\begin{keywords}
	galaxy clusters, dark matter, statistics 
\end{keywords}

\input{illustris_main_text}

\bibliographystyle{mnras}
\bibliography{galaxyDMoffset,Rpackage}
\appendix
\input{illustris_appendix}

\clearpage\bsp\label{lastpage} 
\end{document}

